# Reproducible Research: Peer Assessment 1  



## Loading and preprocessing the data
```{r,echo=TRUE}
data<-read.csv("activity.csv",header = TRUE)
dataWithNa<-data
data<-na.exclude(data)
library(plyr)
dataStepsPerDay<-ddply(data, .(date), summarise, TotalSteps = sum(steps))
dataMeansMediansPerDay<-ddply(data, .(date), summarise, TotalMeans = mean(steps), TotalMedian = median(steps))
```

## Total Steps
```{r,echo=TRUE}
library(lattice)
histogram(dataStepsPerDay$TotalSteps, main="Frequency of Steps", breaks = 53, xlab = "Number of Steps in a day")
```

## What is mean total number of steps taken per day?
Median:  
```{r, echo=TRUE}
median(dataMeansMediansPerDay$TotalMedian)
```

Mean:  
```{r, echo=TRUE}
mean(dataMeansMediansPerDay$TotalMeans)
```

## What is the average daily activity pattern?
1.  
```{r,echo=TRUE}
plot(data$interval,data$steps,type = "l",xaxt = 'n')
axis(1, labels = c('0:00', '5:00', '10:00', '15:00', '20:00'), at = c(0, 500, 1000, 1500, 2000))
```
  
2.  
```{r,echo=TRUE}
dataIntervalPerDay<-ddply(data, .(interval), summarise, TotalSteps = sum(steps))
subset(dataIntervalPerDay, dataIntervalPerDay$TotalSteps==max(dataIntervalPerDay$TotalSteps))$interval
```


## Imputing missing values
Number of NA:  
```{r,echo=TRUE}
sum(is.na(dataWithNa$steps))

```


```{r, echo=TRUE}
# Fill the NA value with the mean of steps
dataWithNa$steps[is.na(dataWithNa$steps)]<-mean(dataMeansMediansPerDay$TotalMeans)
#New data Frame
data<-data.frame(dataWithNa)
dataStepsPerDay<-ddply(data, .(date), summarise, TotalSteps = sum(steps))
histogram(dataStepsPerDay$TotalSteps, main="Frequency of Steps", breaks = 53, xlab = "Number of Steps in a day")
```
  
Mean:  
```{r,echo=TRUE}
mean(data$steps)
```
  
Median:
```{r, echo=TRUE}
median(data$steps)
```
I do not observe any difference. But in the histogram i see a difference in the frequencies. 


## Are there differences in activity patterns between weekdays and weekends?


```{r, echo=TRUE}
#Do not figure out how to just apply a 2 factor weekend method
data<-cbind(data,weekdays(as.Date(data$date)))
```


```{r simulation,echo=TRUE}

plot(data$interval,data[,4],type = "l")
```
