---
output:
  md_document:
    variant: markdown_github
---
# Reproducible Research: Peer Assessment 1  


## Loading and preprocessing the data
```{r initialData,echo=TRUE}
data<-read.csv("activity.csv",header = TRUE)
dataWithNa<-data
data<-na.exclude(data)
library(data.table)
dt <- data.table(data)
dt<-dt[,list(mean=mean(steps),median = median(steps), sum=sum(steps)),by=date]
```

Some summary about the given data.
```{r initialSummary, echo=TRUE}
summary(dataWithNa)
```


## Total Steps
```{r TotalStepsPerDay,echo=TRUE}
library(ggplot2)
c <- ggplot(dt, aes(x=date,y=dt$sum))
c + geom_bar(stat = "identity",width=0.7,color="blue")+ labs(x="Date",y="Steps",title="Total Steps per Day")+ theme_bw(base_size=10)+ theme(axis.text.x=element_blank()) 
```

## What is mean total number of steps taken per day?
Median:  
```{r, echo=TRUE}
median(dt$median)
```

Mean:  
```{r, echo=TRUE}
mean(dt$mean)
```

## What is the average daily activity pattern?
1.  
```{r AvgDiyPattern,echo=TRUE}
#Some Calculations to gather data by interval
dI <- data.table(data)
dI<-dI[,list(mean=mean(steps),median = median(steps), sum=sum(steps)),by=interval]
#Plotting
c <- ggplot(dI, aes(x=interval,y=dI$mean))
c + geom_line() + labs(x="Interval",y="AVG Steps",title="Total Steps Intervals") + theme_bw(base_size=10)
```
  
2.  
```{r maxIntervalsSteps,echo=TRUE}
maxSteps <- max(dI$mean)
maxStepsInterval<-dI[dI$mean==maxSteps,]$interval
```
The interval with the max average is `r maxStepsInterval` with an average of `r maxSteps` steps.

## Imputing missing values
Number of NA:  
```{r,echo=TRUE}
sum(is.na(dataWithNa$steps))

```


Imputing the mean of steps in a new data frame of the NA entries in the data set.
```{r, echo=TRUE}
# Fill the NA value with the mean of steps in a new data frame
dataSet<-data.frame(dataWithNa)
dataSet$steps[is.na(dataSet$steps)]<-mean(dt$mean)
```

```{r, echo = TRUE}
c<-ggplot(dataSet, aes(x=date,y=dataSet$steps))
c+geom_bar(stat = "identity",width=0.7,color="blue")+labs(x="Date",y="Steps",title="Total Steps per Day")+theme_bw(base_size=10) + theme(axis.text.x=element_blank())
```
  
Mean:  
```{r,echo=TRUE}
mean(dataSet$steps)
```
  
Median:
```{r, echo=TRUE}
median(dataSet$steps)
```
There is very little observable difference.

## Are there differences in activity patterns between weekdays and weekends?
```{r, echo=TRUE}
weekd<-factor(c("weekday","weekend"))
dataSet$date<-as.Date(dataSet$date)
dataSet$date<-weekdays(dataSet$date)
## Subset 2 independent dataSets
weekdays<-subset(dataSet, dataSet$date %in% c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday"))
weekends<-subset(dataSet, dataSet$date %in% c("Saturday", "Sunday"))
weekdays$date<-"WeekDay"
weekends$date<-"WeekEnd"
dataSet<-rbind(weekdays,weekends)
dI <- data.table(dataSet)
dI<-dI[,list(mean=mean(steps),median = median(steps), sum=sum(steps),date=date),by=list(interval,date)]
c <- ggplot(dI, aes(x=interval, y=dI$mean, group=date))
c + geom_line() + labs(x="Interval",y="AVG Steps",title="Total Steps Intervals") + theme_bw(base_size=10) + facet_grid(date ~ .)
```


